Stabilization-Free Virtual Element Methods

### 2023-05-31 stabfreevem_sinum.tex
upload referees' reports

\section{Introduction}
\XH{A stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems. The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
$$
c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
$$
for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.  
The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal. 
The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
and improper choices of the stabilization term will produce useless results.
Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems. 
}

Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon \XH{and generally the geometry of the polygon}. 
\XH{Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.}
The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}. \XH{By the way, we refer to \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and 
\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.}

The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
the analysis is rather elaborate. 
\XH{
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
This motivates us to construct stabilization-free VEMs in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.
}

The key to construct stabilization-free VEMs is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
\XH{The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.}
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, \XH{based on a regular simplicial tessellation of polytope $K$}, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.

@@

\section{$H(\div)$-Conforming Macro Finite Elements}\label{sec:divmacrofem}
\XH{
In this section we will construct an $H(\div)$-conforming macro finite element space $\mathbb{V}_{k-1}^{\rm div}(K)$ and the corresponding degrees of freedoms in arbitrary dimension, and establish the $L^2$ norm equivalence for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$
\begin{equation*}%\label{eq:Vkm1divnormequiv}
\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation*}
The space $\mathbb{V}_{k-1}^{\rm div}(K)$ and its $L^2$ norm equivalence will be used to prove
the norm equivalence for the virtual element space
\begin{equation*}%\label{intro:gradVknormequiv} 
\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K),
\end{equation*}
where $V_k(K)$ is the nonconforming virtual element space in Section \ref{sec:stabfreencfmvem}, and the conforming virtual element space in Section \ref{sec:stabfreecfmvem}. Here $Q_{K,k-1}^{\div}$ is the computable $L^2$ projector onto the space $\mathbb{V}_{k-1}^{\rm div}(K)$.}

\subsection{$H(\div)$-conforming finite elements}
For a $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\[
\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
\]
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
\end{align}
for $T\in\mathcal T_K$. Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$, \XH{and $\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-3}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable}.
Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.

We also need the lowest order Raviart-Thomas (RT) element space~\cite{RaviartThomas1977,Nedelec1980}
\[
\boldsymbol{V}^{\mathrm{RT}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
\]
\XH{The DoFs are given by
\[
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F,  \quad q\in \mathbb P_{0}(F), F\in\mathcal F(T)
\]
for $T\in\mathcal T_K$.}
Define $\mathring{\boldsymbol{V}}^{\mathrm{RT}}(K):=\boldsymbol{V}^{\mathrm{RT}}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

By (3.5) in \cite{ChenHuang2021divdiv}, we have the direct decomposition
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
\end{equation}
% \XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
\XH{Recall that \cite[(35)]{Chen;Huang:2020Finite}
\begin{equation}\label{eq:20230205}
\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
\end{equation}
}
% Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
% $$
% \boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
% $$
% where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.

\begin{lemma}\label{lem:skwgrad}
For $\boldsymbol{w}\in\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ satisfying $(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\boldsymbol{0}$, it holds $\boldsymbol{w}=\boldsymbol{0}$.
\end{lemma}
\begin{proof}
Since
\begin{equation*}%\label{eq:20220224}  
(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\frac{1}{2}(\nabla\boldsymbol{w})\boldsymbol{x}-\frac{1}{2}(\nabla\boldsymbol{w})^{\intercal}\boldsymbol{x}=\frac{1}{2}\nabla(\boldsymbol{w}\cdot\boldsymbol{x})-\frac{1}{2}(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w},
\end{equation*}
we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which \XH{together with \eqref{eq:20230205}} implies $\boldsymbol{w}=\boldsymbol{0}$.
\end{proof}

@@

\begin{lemma}\label{lem:Vkm1divnormequivalence}
For $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
\begin{equation}\label{eq:Vkm1divnormequivalence}
\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation}
\end{lemma}
\begin{proof}
\XH{By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
$$
h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim  \|\div\boldsymbol{\phi}\|_{-1,K},
$$ 
where
$$
\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
$$
Then we have
\begin{equation}\label{eq:20230201}  
h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
\end{equation}
For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
$$
h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \|\boldsymbol{\phi}\|_{0,T}+h_T|\boldsymbol{\phi}|_{1,T}\lesssim \|\boldsymbol{\phi}\|_{0,T}.
$$ 
This means
$$
\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
$$ 
Combining \eqref{eq:20230201}, the Cauchy-Schwarz inequality and the last inequality yields
$$
h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
$$
}
% \begin{align*}
% &\quad h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\\
% &\lesssim \|\div\boldsymbol{\phi}\|_{-1,K} + \|\boldsymbol{\phi}\|_{0,K} \lesssim \|\boldsymbol{\phi}\|_{0,K}.    
% \end{align*}

>>>>

\section{Introduction}
A stabilization term is usually required in the virtual element methods (VEMs) to ensure the coercivity of the discrete bilinear form \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014}, while the stabilization term also brings about some problems. The local stabilization term $S_K(\cdot, \cdot)$ has to satisfy 
$$
c_{*} |v|_{1,K}^2\leq S_K(v,v)\leq c^{*} |v|_{1,K}^2 
$$
for $v$ belongs to the non-polynomial subspace of the virtual element space, which influences the condition number of the stiffness matrix and brings in the pollution factor $\frac{\max\{1, c^*\}}{\min\{1, c_*\}}$ in the error estimates \cite{DassiMascotto2018,BeiraodaVeigaDassiRusso2017,Mascotto2018}.  
The stabilization term appears in both sides of the a posteriori error estimates when bounding the error by the residual error estimators \cite{CangianiGeorgoulisPryerSutton2017}.
For the a posteriori error analysis on anisotropic polygonal meshes in \cite{AntoniettiBerroneBorioDAuriaEtAl2022}, the stabilization dominates the error estimator, which makes the anisotropic a posteriori error estimator suboptimal. 
The stabilization term significantly affects the performance of the VEM for the Poisson eigenvalue problem \cite{BoffiGardiniGastaldi2020},
and improper choices of the stabilization term will produce useless results.
Special stabilization terms are designed for a nonlinear elasto-plastic deformation problem \cite{HudobivnikAldakheelWriggers2019} and an electromagnetic interface problem in three dimensions \cite{CaoChenGuo2023}, which are not easy to be extended to other problems.

Recently a stabilization-free linear VEM, based on a higher order polynomial projection of the gradient of virtual element functions, is devised for the Poisson equation in two dimensions in \cite{BerroneBorioMarcon2021}, where the degree of polynomial used in the projection depends on the number of vertices of the polygon and generally the geometry of the polygon. 
Numerical examples in \cite{BerroneBorioMarcon2022} show that the stabilization-free VEM in \cite{BerroneBorioMarcon2021} outperforms the standard VEM in \cite{BeiraodaVeigaBrezziMariniRusso2016} for anisotropic elliptic problems on general convex polygonal meshes.
The stabilization-free VEM in \cite{BerroneBorioMarcon2021} is then applied to solve the Laplacian eigenvalue problem \cite{MengWangBuMei2022}. Along this line, similar stabilization-free virtual element methods are devised for a plane elasticity problem in~\cite{DAltriMirandaPatrunoSacco2021,ChenSukumar2022,ChenSukumar2023}. By the way, we refer to \cite{CicuttinErnLemaire2019} for a stabilization-free hybrid high-order method, and 
\cite{YeZhang2020,AlTaweelWang2020,AlTaweelWang2020a,YeZhang2021,YeZhang2021a,AlTaweelWangYeZhang2021} for stabilization-free weak Galerkin finite element methods.

The idea in \cite{BerroneBorioMarcon2021} is difficult to be extended to construct stabilization-free virtual element methods in higher dimensions, and
the analysis is rather elaborate. 
% This motivates us to construct a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions in arbitrary degree of polynomial  in a unified way.
This motivates us to construct stabilization-free VEMs in arbitrary degree of polynomial, including a nonconforming VEM in arbitrary dimension and a conforming VEM in two dimensions,  in a unified way.

The key to construct stabilization-free VEMs is to find a finite-dimensional space $\mathbb{V}(K)$ for polytope $K$ and a projector $Q_K$ onto the space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
The hidden constants in \eqref{intro:gradVknormequiv} are independent of the size of $K$, but depend on the degree of polynomials, and the chunkiness parameter and the geometric dimension of $K$; see Section~\ref{sec:meshcondition} for details.
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies that the space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually required to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, based on a regular simplicial tessellation of polytope $K$, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as the usual ones.

@@

\section{$H(\div)$-Conforming Macro Finite Elements}\label{sec:divmacrofem}
In this section we will construct an $H(\div)$-conforming macro finite element space $\mathbb{V}_{k-1}^{\rm div}(K)$ and the corresponding degrees of freedoms in arbitrary dimension, and establish the $L^2$ norm equivalence for $\boldsymbol{\phi}\in\mathbb{V}_{k-1}^{\rm div}(K)$
\begin{equation*}%\label{eq:Vkm1divnormequiv}
\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F(K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation*}
The space $\mathbb{V}_{k-1}^{\rm div}(K)$ and its $L^2$ norm equivalence will be used to prove
the norm equivalence for the virtual element space
\begin{equation*}%\label{intro:gradVknormequiv} 
\|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K),
\end{equation*}
where $V_k(K)$ is the nonconforming virtual element space in Section \ref{sec:stabfreencfmvem}, and the conforming virtual element space in Section \ref{sec:stabfreecfmvem}. Here $Q_{K,k-1}^{\div}$ is the computable $L^2$ projector onto the space $\mathbb{V}_{k-1}^{\rm div}(K)$.

\subsection{$H(\div)$-conforming finite elements}
For a $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\[
\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
\]
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x} \label{BDMdof3}
\end{align}
for $T\in\mathcal T_K$. Here $\mathbb P_{k-2}(T)/\mathbb R:=\mathbb P_{k-2}(T)\cap L_0^2(T)$, and $\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-3}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.
Define $\mathring{\boldsymbol{V}}_{k-1}^{\mathrm{BDM}}(K):=\boldsymbol{V}_{k-1}^{\mathrm{BDM}}(K)\cap \boldsymbol{H}_0(\div, K)$.

We also need the lowest order Raviart-Thomas (RT) element space~\cite{RaviartThomas1977,Nedelec1980}
\[
\boldsymbol{V}^{\mathrm{RT}}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
\]
The DoFs are given by
\[
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F,  \quad q\in \mathbb P_{0}(F), F\in\mathcal F(T)
\]
for $T\in\mathcal T_K$.
Define $\mathring{\boldsymbol{V}}^{\mathrm{RT}}(K):=\boldsymbol{V}^{\mathrm{RT}}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

By (3.5) in \cite{ChenHuang2021divdiv}, we have the direct decomposition
\begin{equation}\label{eq:Pkvectordecomp}  
\mathbb P_{k-1}(T;\mathbb R^{d})=\nabla\mathbb P_k(T)\oplus\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}.
\end{equation}
% \XH{where $\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}:=\{\boldsymbol{\tau}\boldsymbol{x}: \boldsymbol{\tau}\in \mathbb P_{k-2}(T;\mathbb K)\}$ with $\boldsymbol{x}\in T$ being the independent variable.}
Recall that \cite[(35)]{Chen;Huang:2020Finite}
\begin{equation}\label{eq:20230205}
\mathbb P_{k}(T)\cap\ker(I+\boldsymbol{x}\cdot\nabla)=\{0\}.
\end{equation}
% Indeed, \eqref{eq:20230205} follows from the Euler's formula \cite[(2.1)]{ChenHuang2021divdiv}
% $$
% \boldsymbol{x}\cdot\nabla q=kq\quad\forall~q\in \mathbb H_k(T),
% $$
% where $\mathbb H_k(T)$ is the space of homogeneous polynomials of degree $k$.

\begin{lemma}\label{lem:skwgrad}
For $\boldsymbol{w}\in\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$ satisfying $(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\boldsymbol{0}$, it holds $\boldsymbol{w}=\boldsymbol{0}$.
\end{lemma}
\begin{proof}
Since
\begin{equation*}%\label{eq:20220224}  
(\skw\nabla\boldsymbol{w})\boldsymbol{x}=\frac{1}{2}(\nabla\boldsymbol{w})\boldsymbol{x}-\frac{1}{2}(\nabla\boldsymbol{w})^{\intercal}\boldsymbol{x}=\frac{1}{2}\nabla(\boldsymbol{w}\cdot\boldsymbol{x})-\frac{1}{2}(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w},
\end{equation*}
we acquire from $\boldsymbol{w}\cdot\boldsymbol{x}=0$ that $(I+\boldsymbol{x}\cdot\nabla)\boldsymbol{w}=\boldsymbol{0}$, which together with \eqref{eq:20230205} implies $\boldsymbol{w}=\boldsymbol{0}$.
\end{proof}

@@

\begin{lemma}\label{lem:Vkm1divnormequivalence}
For $\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K)$, it holds the norm equivalence
\begin{equation}\label{eq:Vkm1divnormequivalence}
\|\boldsymbol{\phi}\|_{0,K}\eqsim h_K\|\div\boldsymbol{\phi}\|_{0,K} + \sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}.
\end{equation}
\end{lemma}
\begin{proof}
By the inverse inequality \cite{Ciarlet1978,Verfuerth2013} (see also \cite[Lemma 10]{Huang2020}),
$$
h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim  \|\div\boldsymbol{\phi}\|_{-1,K},
$$ 
where
$$
\|\div\boldsymbol{\phi}\|_{-1,K}=\sup_{v\in H_0^1(K)}\frac{(\div\boldsymbol{\phi}, v)_K}{|v|_{1,K}}=-\sup_{v\in H_0^1(K)}\frac{(\boldsymbol{\phi}, \nabla v)_K}{|v|_{1,K}} \leq \|\boldsymbol{\phi}\|_{0,K}.
$$
Then we have
\begin{equation}\label{eq:20230201}  
h_K\|\div\boldsymbol{\phi}\|_{0,K}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
\end{equation}
For $F\in\mathcal F^{\partial}(\mathcal T_K)$, there exists a simplex $T\in\mathcal T_K$ satisfying $F\subset\partial T$, then apply the trace inequality \cite[Theorem 1.5.1.10]{Grisvard1985} (see also \cite[(2.18)]{BrennerSung2018}) and the inverse inequality to get
$$
h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \|\boldsymbol{\phi}\|_{0,T}+h_T|\boldsymbol{\phi}|_{1,T}\lesssim \|\boldsymbol{\phi}\|_{0,T}.
$$ 
This means
$$
\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F} \lesssim \sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}\|\boldsymbol{\phi}\|_{0,T}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
$$ 
Combining \eqref{eq:20230201}, the Cauchy-Schwarz inequality and the last inequality yields
$$
h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\lesssim \|\boldsymbol{\phi}\|_{0,K}.
$$
% \begin{align*}
% &\quad h_K\|\div\boldsymbol{\phi}\|_{0,K}+\sup_{\boldsymbol{\psi}\in\div\mathring{\boldsymbol{V}}_{k}^{d-2}(K)}\frac{(\boldsymbol{\phi}, \boldsymbol{\psi})_K}{\|\boldsymbol{\psi}\|_{0,K}} +\sum_{F\in\mathcal F^{\partial}(\mathcal T_K)}h_F^{1/2}\|\boldsymbol{\phi}\cdot\boldsymbol{n}\|_{0,F}\\
% &\lesssim \|\div\boldsymbol{\phi}\|_{-1,K} + \|\boldsymbol{\phi}\|_{0,K} \lesssim \|\boldsymbol{\phi}\|_{0,K}.    
% \end{align*}
